SST_patterns

### 2020-01-31 SST_patterns.Rmd
intensity

@@

@@

>>>>

```{r}
load("Data/OISST_final.RData")
load("Data/CMC_final.RData")
load("Data/SACTN_upwell_base.RData")
load("Data/MUR_final.RData")
load("Data/G1SST_final.RData")
---
title: "SST_patterns"
author: "Amieroh Abrahams"
date: "19 August 2019"
output: html_document
---
# This script is for all the various datasets

@@

ggplot(CMC_dur, aes(duration, colour = product)) +
  geom_freqpoly() +
  facet_wrap(~
month_year_func <- function(df){
  month_year_func<- df %>% 
    mutate(month = month(date_start, abbr = T, label = T)) %>% 
    separate(date_start, into = c("year", "month_no")) %>% 
    unite(month_year, month,year)
    # Now need to get the year into a seperate column from the start date. So now date_start is split in the dataset
}

#### test <- cor(combined_freq_spread$`10`, combined_freq_spread$`30`)

@@

### Looking at intensity

filt_func <- function(df){
  intens <- df %>% 
  #mutate(year = year(date_start)) %>% 
  filter(year(date_start) %in% seq(2011, 2012))
}

filt_func2 <- function(df){
  intens1 <- df %>% 
  #mutate(year = year(date_start)) %>% 
  filter(year(date_start) %in% seq(2013, 2014))
}

OISST_filt_func <- filt_func(OISST_final)
OISST_filt_func2 <- filt_func2(OISST_final)
OISST_binding <- rbind(OISST_filt_func,OISST_filt_func2) %>% 
  select(site, product, intensity_mean)

MUR_filt_func <- filt_func(MUR_final)
MUR_filt_func2 <- filt_func2(MUR_final)
MUR_binding <- rbind(MUR_filt_func,MUR_filt_func2) %>% 
  select(site, product, intensity_mean)

G1SST_filt_func <- filt_func(G1SST_final)
G1SST_filt_func2 <- filt_func2(G1SST_final)
G1SST_binding <- rbind(G1SST_filt_func,G1SST_filt_func2) %>% 
  select(site, product, intensity_mean)

CMC_filt_func <- filt_func(CMC_final)
CMC_filt_func2 <- filt_func2(CMC_final)
CMC_binding <- rbind(CMC_filt_func,CMC_filt_func2) %>% 
  select(site, product, intensity_mean)

#write.csv(SACTN_upwell_base ,'SACTN_upwell_base .csv') # Copied this and then added in a product
rm(SACTN_upwell_base)
SACTN_mean_intensity <- SACTN_upwell_base_ %>% 
  select(site, product, intensity_mean)

Complete_mean_intensity <- rbind(CMC_binding,OISST_binding, G1SST_binding, MUR_binding) %>% 
  select(-heading, - distance, - lat, -lon)
# write.csv(Complete_mean_intensity ,'Complete_mean_intensity .csv') # Copied this and then removedsome columnss

final_intensity <- rbind(SACTN_mean_intensity, Complete_mean_intensity_)

ggplot(data = final_intensity, aes(x = product, y = intensity_mean)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~site)

ggplot(data =final_intensity, aes(x = intensity_mean)) +
  geom_histogram(aes(fill = product),  
                       position = "dodge", alpha=0.6) +
  # labs(x = "Duration (Days)", y = "Number of upwelling signals", colour = "Temperature products") +
  facet_wrap(~site) +
theme_bw() 
```
